Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-09 Papers/ms.tex
reproducibility

\subsection{Reproducibility of the results}
The ``effective sample size'' returned by DNest, which we have described as the
number of posterior samples
reproducibility of the results from the sampling and the effective sample size}.

>>>>

\subsection{Reproducibility of the results}
The ``effective sample size'' returned by DNest, which we have described as the
number of posterior samples, takes into account the fact DNest's target
distribution is not the posterior. However, it does not take autocorrelation
into account, and thus can present an optimistic picture of the accuracy of
any Monte Carlo estimates of posterior expectations. Most standard diagnostic
techniques used in MCMC can be applied here. The simplest of these is a
check of reproducibility. If different runs yield substantially different
results, the MCMC output should be treated with caution.
